Analysis of split plot design using lme4

### 2017-08-24 lme4_analysis.Rmd
Update lme4 analysis to use updated data frames
- Rerun lme4 analysis with corrected data frames

>>>>

### Tiller Sheath Blight Incidence

In 2015 both the nitrogen rates, N100 and N120, were significant when compared with the base N0 rate, water management was not significant.

In 2016 the nitrogen rate N180, was significantly different than the base N60 rate, water management was not significant.

### Tiller Sheath Blight Severity

In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.

In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the base flooding treatment.

### Leaf Sheath Blight Severity

In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.

In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the base treatment for leaf sheath blight severity.
